\begin{abstract}
Current video-language models assume the full recording is available before answering a question. They cannot operate on a live camera feed.
We present \ours, a streaming system for interactive question answering on video that is still in progress.
Its Semantic Keyframe Memory (SKM) keeps at most $N$ frames, scoring each by visual novelty and temporal coverage so that important moments stay and redundant ones get evicted.
A Temporal Query Router (TQR) classifies each question as \emph{instantaneous}, \emph{recent}, or \emph{historical} and passes only the matching time slice to a two-stage Stream-Fused Generator (SFG): BLIP extracts captions and visual answers from selected keyframes, and Flan-T5 fuses those observations into a single response.
To drive evaluation, we introduce \emph{LiveQA-Bench}, a 1{,}500+ question benchmark over 31 diverse video streams---spanning sports highlights, cinematic action, nature, urban, and daily-life scenarios---with per-question scope labels; the first VideoQA benchmark that enforces causal access with explicit temporal scope annotations.
Per-scope results on a T4 GPU reveal clear differentiation: \ours scores 84.0\% on instant queries where a single frame suffices, 61.1\% on historical queries requiring long-range memory, and 33.3\% on recent queries---the hardest scope for all methods.
Ablation by question type shows that SKM benefits historical queries ($+$1.8 points over FIFO), while the keyword-based TQR hurts recent queries by misrouting; disabling it raises overall accuracy to 67.5\% at the cost of 34\% more latency, motivating a learned scope classifier.
Comparison with published results on OVO-Bench and EgoSchema confirms that streaming-aware architectures substantially outperform adapted offline models, and that backward tracing---where importance-scored memory excels---remains the key bottleneck.
Code, LiveQA-Bench, and a live webcam demo will be released.
\end{abstract}
