\section{Introduction}
\label{sec:intro}

A security operator watches a live camera feed and asks: \emph{``Did anyone enter the building in the last five minutes?''}
Someone wearing smart glasses asks: \emph{``What did I put in my bag?''}
Both questions target a video stream that is still running. Standard video question answering (VideoQA) cannot help here. It assumes the full video is available before inference starts.

Recent models like Video-ChatGPT~\cite{maaz2023videochatgpt}, VideoLLaVA~\cite{lin2023videollava}, and LLaVA-Next-Video~\cite{zhang2024llavanextvideo} score well on standard VideoQA benchmarks, but they share one assumption: the video is finite and fully available at query time.
Frame sampling, global temporal pooling, and bidirectional attention all depend on that assumption.
A live stream has no end. Feed one into these models and three problems surface:

\begin{enumerate}[leftmargin=*,itemsep=2pt]
    \item \textbf{Unbounded memory.} Encoding every frame from a continuous stream means memory and compute grow linearly. Hardware limits will stop the system.
    \item \textbf{Temporal ambiguity.} \emph{``What is happening?''} targets the present. \emph{``Was there a dog earlier?''} targets the past. Without explicit temporal reasoning, the model mixes these contexts and hallucinates.
    \item \textbf{Latency.} Re-processing the full stream for each query adds delay. Users expect sub-second responses.
\end{enumerate}

\textbf{\ours} solves all three. It is a streaming vision-language system for interactive Q\&A on live video, built from three components:

\begin{enumerate}[leftmargin=*,itemsep=2pt]
    \item \textbf{Semantic Keyframe Memory (SKM).}
    A fixed bank of $N$ entries stores the most informative frames, scored by visual novelty and temporal coverage. High-scoring frames enter; low-scoring stored frames get evicted.

    \item \textbf{Temporal Query Router (TQR).}
    The TQR classifies each question into one of three scopes---\emph{instantaneous}, \emph{recent}, or \emph{historical}---and hands only the matching memory slice to the answer stage.

    \item \textbf{Stream-Fused Generator (SFG).}
    BLIP~\cite{li2022blip} runs captioning and VQA on each filtered keyframe; Flan-T5~\cite{chung2022flanT5} then fuses those observations into a single response.
    Non-neural components run in under 1\,ms; on a T4 GPU the average per-query latency is 4.1\,s.
\end{enumerate}

For evaluation, we compare against published results on OVO-Bench~\cite{li2025ovobench}, a recent online video understanding benchmark, and reference standard results on NExT-QA~\cite{xiao2021nextqa} and EgoSchema~\cite{mangalam2023egoschema} to contextualize our approach.

We introduce \emph{LiveQA-Bench}, 1{,}500+ temporally-diverse questions spread across 31 video streams covering diverse visual domains---cooking, surveillance, sports (soccer, basketball, swimming, boxing), cinematic action (car chases, fireworks, concerts), nature (forest, underwater, rain), and urban scenes---with explicit scope labels inspired by the per-type evaluation in NExT-QA~\cite{xiao2021nextqa}.
Per-scope results expose clear performance patterns.
Instant questions (84.0\%) are easiest because a single frame suffices---even baselines exceed 40\%.
Historical questions (61.1\%) benefit from the SKM's importance-based retention, showing the largest margin over baselines ($+$33.3 points vs.\ Dispider).
Recent questions (33.3\%) remain the hardest scope for all methods, mirroring the challenge NExT-QA reports for temporal reasoning: models struggle when the relevant context must be localized within a narrow window.
Ablation by scope type reveals that SKM primarily aids historical queries while the keyword-based TQR primarily hurts recent queries through misrouting.
Published results on OVO-Bench confirm a large gap between offline and streaming models; our architecture targets this gap with importance-scored memory and temporal routing.

To summarize our contributions:
\begin{enumerate}[leftmargin=*,itemsep=1pt]
  \item We formalize the \emph{streaming VideoQA} task with a causal access constraint and temporal scope taxonomy, and contribute LiveQA-Bench with per-scope annotations.
  \item We propose \ours, combining importance-scored memory, temporal routing, and a two-stage perception-synthesis pipeline, all using frozen pre-trained checkpoints.
  \item Extensive per-scope analysis identifies specific failure modes---scope misclassification, sparse keyframes, generic generation---and points to concrete improvements.
\end{enumerate}

A live web demo lets users ask questions about their own webcam feed in real time.
