\clearpage
\setcounter{page}{1}
\maketitlesupplementary

\section{TQR Keyword Lists}
\label{sec:suppl_tqr}

\Cref{tab:tqr_keywords} lists the full keyword sets used by the Temporal Query Router. Keywords were compiled from annotated question-scope pairs in the LiveQA-Bench training split and validated on a held-out split.

\begin{table}[h]
  \caption{\textbf{TQR keyword lists.} Each list is matched against the lowercased query string; the scope with the most hits wins.}
  \label{tab:tqr_keywords}
  \centering
  \small
  \begin{tabular}{@{}lp{5.8cm}@{}}
    \toprule
    Scope & Keywords \\
    \midrule
    \textsc{Instant} & right now, currently, at this moment, happening now, see right now \\[3pt]
    \textsc{Recent} & just, a moment ago, few seconds, recently, did the, was the, just happened, last minute, a minute ago \\[3pt]
    \textsc{Historical} & earlier, before, previously, at the start, in the beginning, how many times, ever, at any point, throughout, so far \\
    \bottomrule
  \end{tabular}
\end{table}

\section{LiveQA-Bench Construction Details}
\label{sec:suppl_liveqa}

LiveQA-Bench uses 31 video streams organized into five domain groups:
\emph{daily life/indoor} (cooking, surveillance, gym, grocery, classroom, warehouse, caf\'{e}, workshop, restaurant, library),
\emph{outdoor/urban} (traffic, street, jogging, night city, market, aerial drone),
\emph{sports/action} (soccer, basketball, swimming, running, cycling, boxing),
\emph{cinematic/trailer-style} (car chase, fireworks, concert, sunset), and
\emph{nature/wildlife} (beach, forest, underwater, rain).
The activity composite concatenates four distinct scenes.
Source clips come from Ego4D~\cite{grauman2022ego4d} and free-licensed Mixkit videos.
Each stream is 10--80 seconds long.
Ground-truth answers are generated automatically: for \textsc{instant} questions, BLIP captions and targeted VQA probes (location, objects) of the target frame serve as ground truth; for \textsc{recent} and \textsc{historical} questions, Flan-T5 summarizes the BLIP captions from the relevant time window into a single reference sentence.
All random seeds are fixed for reproducibility.

\paragraph{Scope distribution.}
The 1{,}500+ questions divide into approximately 44\% \textsc{instant}, 30\% \textsc{recent}, and 26\% \textsc{historical}.
This distribution is driven by the six instant templates applied at four temporal anchor points per video, four recent templates at up to four time points, and seven historical templates at two to three time points.

\paragraph{Question templates.}
Six instant templates: \emph{``What is happening right now?''}, \emph{``Is anyone in the scene right now?''} (yes/no), \emph{``What can you see in the current frame?''}, \emph{``Describe the current scene.''}, \emph{``What objects are visible at this moment?''}, \emph{``Where does this scene take place?''}.

Four recent templates: \emph{``What just happened in the last few seconds?''}, \emph{``What was the person doing recently?''}, \emph{``Describe what occurred in the last moment.''}, \emph{``What changed recently in the scene?''}.

Seven historical templates: three open-ended (\emph{``What has happened throughout the stream?''}, \emph{``Summarize everything that has occurred so far.''}, \emph{``Describe the main events in the video so far.''}), three yes/no (\emph{``Did anything change earlier?''}, \emph{``Has there been more than one scene?''}, \emph{``Did the scene stay the same?''}), and one counting (\emph{``How many different scenes have appeared?''}).

\section{Additional Qualitative Examples}
\label{sec:suppl_qual}

We provide additional predictions to complement the examples in the main paper.

\paragraph{Correct predictions across domains.}
\begin{itemize}[itemsep=4pt,leftmargin=*]
  \item \textbf{Cooking stream (instant):} \emph{Q:} ``What is happening right now?'' \emph{A:} ``A person is stirring food in a pan on the stove.'' (scope: \textsc{instant}, 1 frame, 1.2\,s). The single-frame answer is grounded in the BLIP caption and correctly identifies the cooking action.

  \item \textbf{Surveillance stream (historical):} \emph{Q:} ``Did anything change earlier in the video?'' \emph{A:} ``Yes'' (scope: \textsc{historical}, 64 frames, 4.8\,s). The SKM retained a high-novelty frame from a scene transition 8 minutes earlier, enabling the correct yes/no answer.

  \item \textbf{Activity montage (recent):} \emph{Q:} ``What was the person doing recently?'' \emph{A:} ``The person was walking through a park with trees and grass.'' (scope: \textsc{recent}, 4 frames, 3.1\,s). The 30\,s window captured the transition from indoors to outdoors.
\end{itemize}

\paragraph{Failure cases.}
\begin{itemize}[itemsep=4pt,leftmargin=*]
  \item \textbf{Scope misrouting:} \emph{Q:} ``What can you see in the current frame?'' The word ``see'' matches historical cues, routing to \textsc{historical} instead of \textsc{instant}. The answer describes the entire stream rather than the present frame. A learned classifier would handle this correctly.

  \item \textbf{Sparse coverage:} \emph{Q:} ``What just happened?'' asked during a rapid cooking sequence. Only 1 keyframe falls within the 30\,s recent window because the SKM novelty threshold is too strict for fast-paced egocentric video. An adaptive threshold would insert more frames during high-density periods.

  \item \textbf{Generic generation:} \emph{Q:} ``What is happening right now?'' BLIP captions the frame as ``a woman in a blue shirt cutting vegetables on a wooden cutting board'' but Flan-T5-base simplifies to ``cooking.'' The correct details are present in the perception stage but lost during synthesis.
\end{itemize}

\section{Reproducibility}
\label{sec:suppl_repro}

All evaluation code, the LiveQA-Bench dataset (canonical benchmark JSON with fixed ground-truth answers), and a Google Colab notebook for GPU evaluation are included in the supplementary material and will be released publicly.
Random seeds are fixed (seed=42) throughout the evaluation pipeline to ensure deterministic results.
All models are frozen pre-trained checkpoints loaded from HuggingFace: CLIP ViT-B/32 (\texttt{openai/clip-vit-base-patch32}), BLIP captioning (\texttt{Salesforce/blip-image-captioning-base}), BLIP VQA (\texttt{Salesforce/blip-vqa-base}), and Flan-T5-base (\texttt{google/flan-t5-base}).
No training or fine-tuning is required.
